%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to Overleaf --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you open the
% 'Share' menu, you can invite other users to edit at the same
% time. See www.overleaf.com/learn for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{hyperref}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,        
    citecolor=black,
    pdfborderstyle={/S/U/W 1} % Underlines the links instead of a box
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kuber Mehta} & \faEnvelope\ \href{mailto:kuberhob@gmail.com}{kuberhob@gmail.com} \\
    \href{https://kuberwastaken.github.io/}{kuberwastaken.github.io} & \faLinkedin\ \href{https://linkedin.com/in/kubermehta}{kubermehta} \hspace{5pt}
  \faGithub\ \href{https://github.com/kuberwastaken}{kuberwastaken} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section*{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Birla Institute of Technology and Science, Pilani}{Pilani, India}
    {Bachelor of Science in Computer Science}{Aug 2024 -- 2027}
  \resumeSubheading
    {Dr. Akhilesh Das Institute of Professional Studies}{New Delhi, India}
    {Bachelor of Technology in Artificial Intelligence and Data Science}{Aug 2024 -- 2028}
\resumeSubHeadingListEnd

%-----------COURSES------------------
\section*{Courses}
\begin{itemize}[leftmargin=0.15in]
  \item \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/AS9JOBALFZSL}{Google Data Analytics Specialization}} \hfill \textit{Google}\\
  \begin{itemize}[leftmargin=0.2in]
    \item Gained proficiency in data cleaning, analysis, and visualization.
    \item Used tools like SQL, Tableau, and R to create dashboards.
  \end{itemize}

  \item \textbf{\href{https://certificates.cs50.io/fe4b0a5a-c586-4a15-91ec-6b8a65f829e4.pdf?size=letter}{CS50x - Computer Science }} \hfill \textit{Harvard University}\\
  \begin{itemize}[leftmargin=0.2in]
    \item Mastered computer science fundamentals with C, Python, and Flask.
    \item Solved real-world problem sets in various domains.
  \end{itemize}

  \item \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/GIPG5MXXA0FZ}{Databases for Data Scientists Specialization}} \hfill \textit{University of Colorado Boulder}\\
  \begin{itemize}[leftmargin=0.2in]
    \item Mastered relational database design and advanced SQL.
    \item Worked with Google BigQuery for analyzing large datasets.
  \end{itemize}
\end{itemize}


%-----------PROJECTS-----------------
\section*{Projects}
\renewcommand{\baselinestretch}{1.2}
\large
\resumeSubHeadingListStart
  \resumeItem{\href{https://www.trytreat.tech/}{TREAT}}{Developed and deployed a Gradio-based web app to analyze movie and show scripts for potential triggers, powered by Meta Llama-3.2, with an open-source model fully designed and built by me.}
  \resumeItem{\href{https://github.com/Kuberwastaken/ORCUS}{ORCUS}}{Developed an open-source AI system with RoBERTa-OpenAI-Detector and GPT-2 using Flask and React to flag AI-generated LinkedIn comments and promote content authenticity.}
  \resumeItem{\href{https://www.kaggle.com/code/kubermehta/books-reimagined-diary-of-a-wimpy-kid-by-rodrick}{Books Reimagined}}{Developed an AI-powered tool using Google Gemini 1.5 API to transform narrative perspectives in books, enabling character-specific rewrites for any literature.}
  \resumeItem{\href{https://github.com/Kuberwastaken/Github-Art}{Github Art}}{Developed a python-based tool that generates pixel art by mapping designs onto GitHub commit history, including the ability to simulate contributions in the past, turning contribution graphs into artistic displays.}
\resumeSubHeadingListEnd
\normalsize

%-----------COMPETETIONS-----------------
\section*{Competitions}
\resumeSubHeadingListStart
\resumeSubheading
    {Roblox DevRel International Gamejam}{Roblox}
    {Best Simulator Game}{}
  \begin{itemize}[leftmargin=0.15in]
      \item Won 'Best Simulator' in the Roblox DevRel Spain Game Jam, competing against 7,000+ developers worldwide with my game 'Candies Simulator.' 
  \end{itemize}

\resumeSubheading
{Dexter Designing League}{3Dexter}
{National Champion}{}
\begin{itemize}[leftmargin=0.15in]
\item Developed a sustainable human colony model for Mars using SketchUp, Blender, and Cura; won India’s largest 3D Printing and Design competition after three rigorous rounds of challenges.
\end{itemize}






%--------PROGRAMMING SKILLS------------
\section*{Programming Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages}{:Python, SQL, C, HTML, CSS, JavaScript, R, LUA}
  }
  \item{
    \textbf{Technologies}{: React, Node, BigQuery, Tableau, TensorFlow, PyTorch, Gradio, Flask}
  }
\resumeSubHeadingListEnd

\end{document}
