\documentclass[letterpaper,10.8pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,        
    citecolor=black,
    pdfborderstyle={/S/U/W 1}
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}  % Changed from -10pt to -5pt for better alignment
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kuber Mehta} & \faEnvelope\ \href{mailto:kuberhob@gmail.com}{kuberhob@gmail.com} \\
    \href{https://kuberwastaken.github.io/}{kuberwastaken.github.io} & \faLinkedin\ \href{https://linkedin.com/in/kubermehta}{kubermehta} \hspace{5pt}
  \faGithub\ \href{https://github.com/kuberwastaken}{kuberwastaken} \\
\end{tabular*}

\section*{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Birla Institute of Technology and Science, Pilani}{Pilani, India}
    {Bachelor of Science in Computer Science}{Aug 2024 -- 2027}
  \resumeSubheading
    {Guru Gobind Singh Indraprastha University}{New Delhi, India}
    {Bachelor of Technology in Artificial Intelligence and Data Science}{Aug 2024 -- 2028}
\resumeSubHeadingListEnd

\section*{Professional Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {\href{https://www.polyth.ink/}{PolyThink}}{New Delhi, India}
    {Founder}{Apr 2025 -- Present}
    \begin{itemize}
      \item Building a multi-agent AI system where multiple models debate and fact-check each other to reduce hallucinations.
      \item Implemented an agentic Solver–Judge framework using AI targeting reliability and transparency in LLM generated solutions.
    \end{itemize}

  \resumeSubheading
    {Perplexity AI}{Remote}
    {Business Fellow}{Mar 2025 -- Present}
    \begin{itemize}
      \item Selected for a highly competitive AI strategy program focused on practical applications and product thinking.
      \item Participated in mentor-led sessions and contributed to projects exploring AI monetization and deployment.
    \end{itemize}

  \resumeSubheading
    {JP Morgan Chase}{Remote}
    {Virtual Experience Intern}{Feb 2025 -- Apr 2025}
    \begin{itemize}
      \item Created a Python-based stock data analysis tool and interactive dashboards.
      \item Used React + TypeScript to build dynamic components using JPMorgan's design systems.
    \end{itemize}

  \resumeSubheading
    {\href{https://trytreat.tech/}{TREAT AI}}{New Delhi India}
    {Founder}{2024 -- Present}
    \begin{itemize}
      \item Built an open-source AI platform with 20+ contributors to flag triggering content in films and shows using LLMs.
      \item Integrated and post trained 20+ models by Gemini, Llama, DeepSeek and more to analyze scripts and deliver personalized flags.
    \end{itemize}
\resumeSubHeadingListEnd

\section*{Achievements}
\resumeSubHeadingListStart
  \resumeSubheading
    {\href{https://media.licdn.com/dms/image/v2/D562DAQG7PINx-24MPA/profile-treasury-image-shrink_800_800/profile-treasury-image-shrink_800_800/0/1723232806730?e=1741608000\&v=beta\&t=UIry8g7Tyj4Lo9cnannvYgDn-ZYgYkDLdvKInLc7XVU}{Roblox DevRel International Gamejam}}{}
    {Best Simulator Game}{}
    \begin{itemize}
      \item Awarded 'Best Simulator' for 'Candies Simulator' among 7,000+ global developers.
    \end{itemize}
    
  \resumeSubheading
    {\href{https://www.kaggle.com/code/kubermehta/books-reimagined-diary-of-a-wimpy-kid-by-rodrick}{Books Reimagined}}{}
    {Top 10 - Kaggle x Google Gemini Long Context Challenge}{}
    \begin{itemize}
    \item Using \textbf{Gemini Long Context} to \textbf{rewrite books from different character perspectives}, ranking \textbf{Top 20} Globally.
    \end{itemize}
\resumeSubHeadingListEnd

\section*{Projects}
\resumeSubHeadingListStart
  \resumeItem{\href{https://github.com/Kuberwastaken/backdooms}{The Backdooms}}{Ported a version of "Doom" inspired by the Backrooms, \textbf{self-contained in a QR code}, less than \textbf{2.7KB} in size with a \textbf{custom compression algorithm}. Achieved \textbf{140,000+ views} in \textbf{48 hours} on LinkedIn.}
  \vspace{5pt}
  \resumeItem{\href{https://github.com/Kuberwastaken/ORCUS}{ORCUS}}{Developed an \textbf{open-source AI system} with \textbf{RoBERTa-OpenAI-Detector} and \textbf{GPT-2} using \textbf{Flask and React} to \textbf{flag AI-generated LinkedIn comments} and promote content authenticity.}
  \vspace{5pt}
  \resumeItem{\href{https://github.com/Kuberwastaken/free-deep-research}{Free Deep Research}}{Created a \textbf{free alternative} to OpenAI's \textbf{Deep Research agent}, replicating most capabilities with \textbf{adjustable breadth and depth} for customization.}
\resumeSubHeadingListEnd

\section*{Notable Courses}
\resumeSubHeadingListStart
  \item \textbf{\href{https://cdn-uploads.huggingface.co/production/uploads/noauth/iD2BAETFKpkiYBWPVz1fn.webp}{Hugging Face Fundamentals of Agents,}} \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/AS9JOBALFZSL}{Google Data Analytics,}} \textbf{\href{https://certificates.cs50.io/fe4b0a5a-c586-4a15-91ec-6b8a65f829e4.pdf?size=letter}{Harvard University CS50x,}}
  \textbf{\href{https://certificates.cs50.io/025b42e2-4fe7-4095-a3d8-0f2ef49e7b1c.pdf?size=letter}{CS50AI}}
\resumeSubHeadingListEnd

\section*{Programming Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages}{: Python, SQL, C, HTML, CSS, JavaScript, R, LUA}
  }
  \item{
    \textbf{Technologies}{: React, NextJS, Node, BigQuery, Tableau, TensorFlow, PyTorch, Gradio, Flask}
  }
\resumeSubHeadingListEnd

\end{document}