\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,        
    citecolor=black,
    pdfborderstyle={/S/U/W 1}
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}  % Changed from -10pt to -5pt for better alignment
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kuber Mehta} & \faEnvelope\ \href{mailto:kuberhob@gmail.com}{kuberhob@gmail.com} \\
    \href{https://kuberwastaken.github.io/}{kuberwastaken.github.io} & \faLinkedin\ \href{https://linkedin.com/in/kubermehta}{kubermehta} \hspace{5pt}
  \faGithub\ \href{https://github.com/kuberwastaken}{kuberwastaken} \\
\end{tabular*}

\section*{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Birla Institute of Technology and Science, Pilani}{Pilani, India}
    {Bachelor of Science in Computer Science}{Aug 2024 -- 2027}
  \resumeSubheading
    {Dr. Akhilesh Das Institute of Professional Studies}{New Delhi, India}
    {Bachelor of Technology in Artificial Intelligence and Data Science}{Aug 2024 -- 2028}
\resumeSubHeadingListEnd

\section*{Professional Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {JP Morgan Chase}{Remote}
    {Virtual Experience Remote Intern}{Feb 2025 -- Present}
    \begin{itemize}
      \item Developing a Python-based interface for real-time stock price data analysis and interactive dashboards.
      \item Integrating React and TypeScript to build dynamic web applications using JPMorgan Chase frameworks.
    \end{itemize}
  \resumeSubheading
    {Perplexity AI}{Remote}
    {Business Fellow}{Feb 2025 -- Present}
    \begin{itemize}
      \item Selected for a competitive program focused on AI applications in business and strategy, developing practical AI skills.
      \item Participating in workshops led by industry leaders and gaining access to an exclusive AI community.
    \end{itemize}
\resumeSubHeadingListEnd

\section*{Projects}
\resumeSubHeadingListStart
  \resumeItem{\href{https://trytreat.tech/}{TREAT}}{Developed and deployed a \textbf{Gradio}-based web app to \textbf{analyze movie and show scripts} for potential \textbf{triggering content}, powered by \textbf{Meta Llama-3.2} and \textbf{DeepSeek R1}, with an \textbf{open-core model}.}
  \resumeItem{\href{https://github.com/Kuberwastaken/backdooms}{The Backdooms}}{Ported a version of "Doom" inspired by the Backrooms, \textbf{self-contained in a QR code}, less than \textbf{2.6KB} in size with a \textbf{custom compression algorithm}. Achieved \textbf{140,000+ views} in \textbf{48 hours} on LinkedIn.}
  \resumeItem{\href{https://github.com/Kuberwastaken/ORCUS}{ORCUS}}{Developed an \textbf{open-source AI system} with \textbf{RoBERTa-OpenAI-Detector} and \textbf{GPT-2} using \textbf{Flask and React} to \textbf{flag AI-generated LinkedIn comments} and promote content authenticity.}
  \resumeItem{\href{https://www.kaggle.com/code/kubermehta/books-reimagined-diary-of-a-wimpy-kid-by-rodrick}{Books Reimagined}}{Developed an \textbf{AI-powered tool} using \textbf{Google Gemini 1.5 API} to \textbf{transform narrative perspectives} in books, enabling \textbf{character-specific rewrites} for any literature.}
\resumeSubHeadingListEnd

\section*{Courses}
\begin{itemize}[leftmargin=0.15in]
  \item \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/AS9JOBALFZSL}{Google Data Analytics Specialization}} \hfill \textit{Google}\\
    Gained proficiency in data cleaning, analysis, and visualization using SQL, Tableau, and R.
  \item \textbf{\href{https://certificates.cs50.io/fe4b0a5a-c586-4a15-91ec-6b8a65f829e4.pdf?size=letter}{CS50x - Computer Science}} \hfill \textit{Harvard University}\\
    Mastered computer science fundamentals with C, Python, and Flask, solving real-world problem sets.
  \item \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/GIPG5MXXA0FZ}{Databases for Data Scientists Specialization}} \hfill \textit{University of Colorado Boulder}\\
    Mastered relational database design and advanced SQL, including Google BigQuery for large datasets.
\end{itemize}

\section*{Achievements}
\resumeSubHeadingListStart
  \resumeSubheading
    {\href{https://media.licdn.com/dms/image/v2/D562DAQG7PINx-24MPA/profile-treasury-image-shrink_800_800/profile-treasury-image-shrink_800_800/0/1723232806730?e=1741608000\&v=beta\&t=UIry8g7Tyj4Lo9cnannvYgDn-ZYgYkDLdvKInLc7XVU}{Roblox DevRel International Gamejam}}{}
    {Best Simulator Game}{}
    \begin{itemize}
      \item Awarded 'Best Simulator' for 'Candies Simulator' among 7,000+ global developers.
    \end{itemize}
\resumeSubHeadingListEnd

\section*{Programming Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages}{: Python, SQL, C, HTML, CSS, JavaScript, R, LUA}
  }
  \item{
    \textbf{Technologies}{: React, Node, BigQuery, Tableau, TensorFlow, PyTorch, Gradio, Flask}
  }
\resumeSubHeadingListEnd

\end{document}
