\documentclass[letterpaper,10.8pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,        
    citecolor=black,
    pdfborderstyle={/S/U/W 1}
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}  % Changed from -10pt to -5pt for better alignment
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kuber Mehta} & \faEnvelope\ \href{mailto:kuberhob@gmail.com}{kuberhob@gmail.com} \\
    \href{https://kuberwastaken.github.io/}{kuberwastaken.github.io} & \faLinkedin\ \href{https://linkedin.com/in/kubermehta}{kubermehta} \hspace{5pt}
  \faGithub\ \href{https://github.com/kuberwastaken}{kuberwastaken} \\
\end{tabular*}

\section*{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Birla Institute of Technology and Science, Pilani}{Pilani, India}
    {Bachelor of Science in Computer Science}{Aug 2024 -- 2027}
  \resumeSubheading
    {Guru Gobind Singh Indraprastha University}{New Delhi, India}
    {Bachelor of Technology in Artificial Intelligence and Data Science}{Aug 2024 -- 2028}
\resumeSubHeadingListEnd

\section*{Professional Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Perplexity AI}{Remote}
    {Business Fellow}{Mar 2025 -- Present}
    \begin{itemize}
      \item Selected for a competitive program focused on AI applications in business and strategy, developing practical AI skills.
      \item Participating in workshops led by industry leaders and gaining access to an exclusive AI community.
    \end{itemize}
\resumeSubheading
  {JP Morgan Chase}{Remote}
  {Virtual Experience Remote Intern}{Feb 2025 -- Apr 2025}
  \begin{itemize}
    \item Developed a Python-based interface for real-time stock price data analysis and interactive dashboards.
    \item Integrated React and TypeScript to build dynamic web applications using JPMorgan Chase frameworks.
  \end{itemize}
\resumeSubHeadingListEnd

\section*{Projects}
\resumeSubHeadingListStart
  \resumeItem{\href{https://trytreat.tech/}{TREAT}}{Developed and deployed a \textbf{Gradio}-based Spaces web app to \textbf{analyze movie and show scripts} for potential \textbf{triggering content}, powered by \textbf{Meta Llama-3.2} and \textbf{DeepSeek R1}, with an \textbf{open-source model}.}
  \vspace{5pt}
  \resumeItem{\href{https://github.com/Kuberwastaken/backdooms}{The Backdooms}}{Ported a version of "Doom" inspired by the Backrooms, \textbf{self-contained in a QR code}, less than \textbf{2.6KB} in size with a \textbf{custom compression algorithm}. Achieved \textbf{140,000+ views} in \textbf{48 hours} on LinkedIn.}
  \vspace{5pt}
  \resumeItem{\href{https://github.com/Kuberwastaken/ORCUS}{ORCUS}}{Developed an \textbf{open-source AI system} with \textbf{RoBERTa-OpenAI-Detector} and \textbf{GPT-2} using \textbf{Flask and React} to \textbf{flag AI-generated LinkedIn comments} and promote content authenticity.}
  \vspace{5pt}
  \resumeItem{\href{https://github.com/Kuberwastaken/free-deep-research}{Free Deep Research}}{Created a \textbf{free alternative} to OpenAI’s \textbf{Deep Research agent}, replicating most capabilities with \textbf{adjustable breadth and depth} for customization.}
\resumeSubHeadingListEnd

\section*{Courses}
\begin{itemize}[leftmargin=0.15in]
  \item \textbf{\href{https://cdn-uploads.huggingface.co/production/uploads/noauth/iD2BAETFKpkiYBWPVz1fn.webp}{Fundamentals of Agents}} \hfill \textit{Hugging Face}\\
    Built AI agents using frameworks like smolagents, LlamaIndex, and LangGraph. leant agent fundamentals, tool integration, and real-world applications.
  \item \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/AS9JOBALFZSL}{Google Data Analytics Specialization}} \hfill \textit{Google}\\
    Gained proficiency in data cleaning, analysis, and visualization using SQL, Tableau, and R.
  \item \textbf{\href{https://certificates.cs50.io/fe4b0a5a-c586-4a15-91ec-6b8a65f829e4.pdf?size=letter}{CS50x - Computer Science}} \hfill \textit{Harvard University}\\
    Mastered computer science fundamentals with C, Python, and Flask, solving real-world problem sets.
\end{itemize}

\section*{Achievements}
\resumeSubHeadingListStart
  \resumeSubheading
    {\href{https://media.licdn.com/dms/image/v2/D562DAQG7PINx-24MPA/profile-treasury-image-shrink_800_800/profile-treasury-image-shrink_800_800/0/1723232806730?e=1741608000\&v=beta\&t=UIry8g7Tyj4Lo9cnannvYgDn-ZYgYkDLdvKInLc7XVU}{Roblox DevRel International Gamejam}}{}
    {Best Simulator Game}{}
    \begin{itemize}
      \item Awarded 'Best Simulator' for 'Candies Simulator' among 7,000+ global developers.
    \end{itemize}
    
  \resumeSubheading
    {\href{https://www.kaggle.com/code/kubermehta/books-reimagined-diary-of-a-wimpy-kid-by-rodrick}{Books Reimagined}}{}
    {Top 10 - Kaggle x Google Gemini Long Context Challenge}{}
    \begin{itemize}
    \item Using \textbf{Gemini Long Context} to \textbf{rewrite books from different character perspectives}, ranking \textbf{Top 20} Globally.
    \end{itemize}
\resumeSubHeadingListEnd

\section*{Programming Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages}{: Python, SQL, C, HTML, CSS, JavaScript, R, LUA}
  }
  \item{
    \textbf{Technologies}{: React, NextJS, Node, BigQuery, Tableau, TensorFlow, PyTorch, Gradio, Flask}
  }
\resumeSubHeadingListEnd

\end{document}
