%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to Overleaf --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you open the
% 'Share' menu, you can invite other users to edit at the same
% time. See www.overleaf.com/learn for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{hyperref}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,        
    citecolor=black,
    pdfborderstyle={/S/U/W 1} % Underlines the links instead of a box
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kuber Mehta} & Email: \href{mailto:kuberhob@gmail.com}{kuberhob@gmail.com} \\
  \faHome\ \href{https://kuberwastaken.github.io/}{kuberwastaken.github.io} & Mobile: +91 9625079109 \\
  \faLinkedin\ \href{https://linkedin.com/in/kubermehta}{/in/kubermehta} \quad 
  \faGithub\ \href{https://github.com/kuberwastaken}{kuberwastaken} & \\
\end{tabular*}

%-----------EDUCATION-----------------
\section*{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Birla Institute of Technology and Science, Pilani}{Pilani, India}
    {Bachelor of Science in Computer Science}{Aug 2024 -- 2027}
  \resumeSubheading
    {Dr. Akhilesh Das Institute of Professional Studies}{New Delhi, India}
    {Bachelor of Technology in Artificial Intelligence and Data Science}{Aug 2024 -- 2028}
\resumeSubHeadingListEnd

%-----------COURSES------------------
\section*{Courses}
\begin{itemize}[leftmargin=0.15in]
  \item \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/AS9JOBALFZSL}{Google Data Analytics Specialization}} \hfill \textit{Google}\\
  \begin{itemize}[leftmargin=0.2in]
    \item Gained proficiency in data cleaning, analysis, and visualization.
    \item Used tools like SQL, Tableau, and R to derive insights and create dashboards.
    \item Completed hands-on assessments simulating real-world data analysis scenarios.
  \end{itemize}

  \item \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/GIPG5MXXA0FZ}{Databases for Data Scientists Specialization}} \hfill \textit{University of Colorado Boulder}\\
  \begin{itemize}[leftmargin=0.2in]
    \item Mastered relational database design and advanced SQL for data manipulation.
    \item Worked with Google BigQuery for analyzing and querying large datasets.
    \item Studied emerging database trends, including NoSQL and distributed databases.
  \end{itemize}

  \item \textbf{\href{https://certificates.cs50.io/fe4b0a5a-c586-4a15-91ec-6b8a65f829e4.pdf?size=letter}{CS50: Introduction to Computer Science}} \hfill \textit{Harvard University}\\
  \begin{itemize}[leftmargin=0.2in]
    \item Mastered computer science fundamentals and core programming concepts.
    \item Introduced to C, Python, Flask, SQL, JavaScript, HTML, and CSS.
    \item Solved real-world problem sets in domains like finance, cryptography, and gaming, enhancing problem-solving skills.
  \end{itemize}
\end{itemize}

%-----------PROJECTS-----------------
\section*{Projects}
\resumeSubHeadingListStart
  \resumeItem{\href{https://github.com/Kuberwastaken/TREAT}{TREAT}}{Developed an AI web application built with Flask and Python using Meta Llama-3.2-1B to analyze movie and show scripts for potential triggers.}
  \resumeItem{\href{https://www.kaggle.com/code/kubermehta/books-reimagined-diary-of-a-wimpy-kid-by-rodrick}{Books Reimagined}}{Developed an AI-powered tool using Google Gemini 1.5 API to transform narrative perspectives in books, enabling character-specific rewrites for any literature.}
  \resumeItem{\href{https://github.com/Kuberwastaken/ROOP-AI-Deepfakes}{ROOP AI Deepfakes}}{Integrated the ROOP AI deepfake model into Google Colab, enabling free, platform-independent video generation in under 7 minutes.}
  \resumeItem{\href{https://github.com/Kuberwastaken/Github-Art}{Github Art}}{Created a tool to make pixel art in GitHub commit history.}
\resumeSubHeadingListEnd

%-----------COMPETETIONS-----------------
\section*{Competitions}
\resumeSubHeadingListStart
\renewcommand{\labelitemi}{$\circ$} % Define open-circle bullet
\resumeSubheading
    {Roblox DevRel International Gamejam}{Roblox}
    {Best Simulator Game}{}
  \begin{itemize}[leftmargin=0.15in]
      \item Won 'Best Simulator' in this game jam by Roblox DevRel Spain, competing against over 7,000 developers worldwide with my game 'Candies Simulator.' 
  \end{itemize}
  
\renewcommand{\labelitemi}{$\circ$} % Define open-circle bullet
\resumeSubheading
  {Concours Romain Rolland, Delhi}{Alliance Française de Normandie, France}
  {Gold Medalist}{}
  \begin{itemize}[leftmargin=0.15in]
    \item Awarded with the State-Level Gold Medal in the prestigious Concours Romain Rolland French Olympiad, representing Delhi, India.
  \end{itemize}

%--------PROGRAMMING SKILLS------------
\section*{Programming Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages}{: SQL, C, CSS, Python, JavaScript}
    \hfill
    \textbf{Technologies}{: React, Node, BigQuery, Tableau, Flask}
  }
\resumeSubHeadingListEnd


\end{document}